Forecasting interrupted time series

### 2024-01-05 fits.qmd
Updated pedestrians example

# Handling interruptions when forecasting

@@

@@

>>>>

# Handling interruptions when forecasting {#sec-methods}

@@

## Example: Pedestrians

```{r}
#| include: false
tar_load(c(raw_walkers, walkers2, lockdowns))
nsensors <- length(unique(raw_walkers$Sensor))
ngoodsensors <- length(unique(walkers2$Sensor))
lockdowns <- lockdowns |>
  mutate(Duration = End - Start + 1)
```

The pedestrian data set is a daily time series showing the number of pedestrians per day in Melbourne, Australia. The data were obtained from the Pedestrian Counting System maintained by the City of Melbourne [@pedestrians], and are based on automated hourly counts from sensors at `r nsensors` locations over the period from `r min(raw_walkers$Date)` to `r max(raw_walkers$Date)`. All sensors had some missing data, and we chose to use sensors with no more than `r 30*24` missing hours, equivalent to 30 days of missing data. This resulted in `r ngoodsensors` sensors being used in the analysis. The data were aggregated to daily counts for each sensor, and then the results were averaged across sensors to obtain a measure of pedestrian traffic per day. The resulting time series is shown in @fig-walkers.

```{r}
#| label: fig-walkers
#| fig-height: 3.7
#| fig-cap: "Pedestrian traffic in Melbourne, Australia, from 2018 to 2023. The gray shaded regions indicate periods of lockdown due to COVID-19."
tar_read(walkers_plot)
```

We have also shown the periods of lockdown due to COVID-19. In Melbourne, there were six separate lockdowns ranging from `r as.numeric(min(lockdowns$Duration))` days to `r as.numeric(max(lockdowns$Duration))` days in length. The first official lockdown period was from 31 March 2020 to `r format(min(lockdowns$End), "%d %b %Y")`, and the last lockdown was from `r format(max(lockdowns$Start), "%d %b %Y")` to `r format(max(lockdowns$End), "%d %b %Y")`. However, the first period was preceded by over a week when most people elected to stay and work at home, so we have chosen to start the first period on `r format(min(lockdowns$Start), "%d %b %Y")`, to better reflect human behaviour. Otherwise, we have used the official lockdown dates.

We apply the four solutions discussed in @sec-methods. We fit ETS, ARIMA and dynamic ARIMA models to the data, with no transformations used. We have evaluated the methods by using time series cross-validation, with the initial training set comprising the whole of 2019, and subsequent training sets growing by 1 week at a time, to the end of 2021. The test sets are always 3 weeks long. Thus, we have evaluated the forecasts during 2020 and 2021, covering all lockdown periods, and the start of the recovery period. The results are shown in @fig-walkers-plot1.

@@

# References
